---
title: "210407_ELT2_targets_spatial_analysis"
author: "IRM"
date: "210407"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Install libraries

```{r}
# install.packages("knitr")
# install.packages("readxl")
# install.packages("tidyverse")
# install.packages("ggpubr")
# install.packages("mratios")
# install.packages("dplyr")
# install.packages("chromoMap")
```


Load libraries

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(mratios)
library(chromoMap)
```

annotated peaks rds file -> data frame

```{r}
elt2_GRange <- readRDS("annotatedPeaks.rds")
elt2_peaks <- as.data.frame(elt2_GRange) %>% rowid_to_column() %>% dplyr::select(-rowid)
```


```{r}
elt2_peaks %>% head()
```

```{r}
colnames(elt2_peaks)
```


filtering for just L1 peaks that = 1 because this means they are changing and the dineen data only looked at L1

```{r}
elt2_peaks_L1_IDR <- elt2_peaks %>%
  filter(L1_IDR == 1)

```

setting up chromosome data for chromoMap format, no row or column names allowed, just chromosome then start and end positions

```{r}
chr_file_2 <- elt2_peaks_L1_IDR %>% 
  select(seqnames, start_position, end_position) %>%
  remove_rownames

chr_file_2$seqnames <- as.character(chr_file_2$seqnames)
class(chr_file_2$seqnames)
chr_file_2$start_position <- as.numeric(chr_file_2$start_position)
class(chr_file_2$start_position)
chr_file_2$end_position <- as.numeric(chr_file_2$end_position)
class(chr_file_2$end_position)

colnames(chr_file_2) <- NULL
```


```{r}
head(chr_file_2)
```


save as a tab delineated text file
```{r}
write.table(chr_file_2, file = "chr_file_2.txt", quote = FALSE, sep="\t")
```



```{r}
head(elt2_peaks_L1_IDR)
```


creating annotated data file

```{r}
bound_genes_class_assignments <- read.table("Bound_Genes_Class_Assignments.txt", header = TRUE, sep = ",", dec = ".")

bound_class_assignments <- as.data.frame(bound_genes_class_assignments)
```


```{r}
merged_peaks_with_class_assignments <- merge(x=bound_class_assignments, y=elt2_peaks_L1_IDR, by.x="WBGeneID", by.y="feature") 

print(merged_peaks_with_class_assignments)
```

```{r}
merged_peaks_and_class <- merged_peaks_with_class_assignments %>% 
  mutate(
  L1_peak_summit_mean = rowMeans(merged_peaks_with_class_assignments[,c('L1_peak_1_summit', 'L1_peak_2_summit')], na.rm=TRUE)
  )

merged_peaks_and_class$seqnames <- as.character(merged_peaks_and_class$seqnames)
merged_peaks_and_class$start_position <- as.numeric(merged_peaks_and_class$start_position)
merged_peaks_and_class$end_position <- as.numeric(merged_peaks_and_class$end_position)

print(merged_peaks_and_class)
```

~trouble shooting class column not being character values wait actually it is~
```{r}
class(merged_peaks_and_class$WBGeneID)
class(merged_peaks_and_class$seqnames)
class(merged_peaks_and_class$start_position)
class(merged_peaks_and_class$end_position)
class(merged_peaks_and_class$class)
```


L1_peak_summit_mean,(not including for the minute because code not working)

```{r}
anno_file_2 <- merged_peaks_and_class %>% 
  select(WBGeneID, seqnames, start_position, end_position, class)

head(merged_peaks_and_class[,c("WBGeneID","seqnames")])

rownames(anno_file_2) <- NULL

colnames(anno_file_2) <- NULL
```


```{r}
head(anno_file_2)
```



save as a tab delineated text file
```{r}
write.table(anno_file_2, file = "anno_file_2.txt", quote = FALSE, sep="\t")
```




chromoMap begins here

```{r}
chr_file <- read.table("ce11.chrom.sizes.txt")

anno_file_2 <- read.table("anno_file_2.txt") %>% dplyr::select(-V1)
anno_file_2
```


```{r}
chromoMap(list(chr_file), list(anno_file_2),
          data_based_color_map = T, 
          data_type = "categorical", 
          legend = T, lg_x = 300,
          lg_y = 300, 
          canvas_width = 1000,
          chr_width = 20,
          chr_length = 7)
```


```{r}

```






